% =============================================================================
% sections/design/safety/software_safety.tex  -  Software Safety Systems
% Teams: software (best guess - unconfirmed) / Status: stub
%
% Nested under "Safety Systems" (section-level subsection).
% Requires \usepackage{tikz} (base tikz only, no extra libraries) and
% \usepackage{tabularx} for compact tables.
% =============================================================================

In addition to the hardware E-Stop, the rover implements layered software safety mechanisms that provide graceful degradation before a hard power cut is needed (Table~\ref{tab:sw-safety-overview}).

\begin{table}[h]
    \footnotesize
    \centering
    \caption{Overview of software safety mechanisms}
    \label{tab:sw-safety-overview}
    \begin{tabularx}{\linewidth}{@{}p{3cm} X p{3cm}@{}}
        \toprule
        \textbf{Mechanism} & \textbf{Behaviour} & \textbf{Trigger} \\
        \midrule
        Remote motor lock & Operator command locks motion; power/telemetry retained & Operator command \\
        Comms-loss rampdown & Bounded deceleration to zero speed & Control link lost \\
        CAN watchdog (ESP) & ESP takes over and stops rover if no motor commands seen within timeout & Main computer / SW fault \\
        Overcurrent cutoff & Wheel driver deactivates above TODO\,\si{\ampere} & Stall / collision \\
        Shock detection & Current-spike + IMU based impact detection & \textit{Planned, not yet implemented} \\
        \bottomrule
    \end{tabularx}
\end{table}

\subsubsection{Watchdogs and Fault Detection}
\label{sec:sw-watchdog}

\paragraph{CAN bus watchdog.} A dedicated ESP monitors the CAN bus for periodic motor speed commands from the main computer. If none arrive within a timeout window of 200\,\si{\milli\second}, the ESP assumes a main-computer/software fault, takes over motor control authority, and decelerates the rover to a stop.

\paragraph{Communication-loss detection.} The ground station sends a periodic heartbeat message every 100\,\si{\milli\second}; if no heartbeat is received within a timeout window, the rover assumes the control link is lost and initiates a controlled deceleration. The target deceleration is \SI{1.2}{\meter\per\second\squared} -- a compromise between stopping quickly and avoiding excessive mechanical stress on the rover's heavy chassis and extended robotic arm.

\subsubsection{Safe-State Transitions / Safety State Machine}
\label{sec:sw-state-machine}

\todo[inline]{This state machine is not yet implemented -- review, adjust, and implement before final submission, or clearly mark as a planned improvement.}

A supervisory state machine is proposed (Fig.~\ref{fig:safety-fsm}), implemented as a ROS2 node (\texttt{safety\_manager}) publishing the current safety state; motor-command nodes gate their output on this state, and leaving \texttt{SOFT\_STOP}/\texttt{RAMPDOWN} requires an explicit operator resume call, preventing unintended autonomous resumption.

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[
        every node/.style={font=\footnotesize},
        state/.style={draw, rounded corners, minimum width=2.4cm, minimum height=0.8cm, align=center}
    ]
        \node[state] (nominal) at (0,0)     {NOMINAL};
        \node[state] (soft)    at (3.4,0)   {SOFT\_STOP};
        \node[state] (ramp)    at (0,-2)    {RAMPDOWN};
        \node[state] (hard)    at (3.4,-2)  {HARD\_ESTOP};

        \draw[->] (nominal) to[bend left=15] node[above,font=\scriptsize]{lock} (soft);
        \draw[->] (soft) to[bend left=15] node[below,font=\scriptsize]{resume} (nominal);
        \draw[->] (nominal) to[bend right=15] node[left,font=\scriptsize]{comms lost} (ramp);
        \draw[->] (ramp) to[bend right=15] node[right,font=\scriptsize]{resume} (nominal);
        \draw[->] (nominal) -- node[font=\scriptsize,sloped,above]{E-Stop} (hard);
        \draw[->] (soft) -- (hard);
        \draw[->] (ramp) -- (hard);
    \end{tikzpicture}
    \caption{Proposed software safety state machine.}
    \label{fig:safety-fsm}
\end{figure}

\subsubsection{Behaviour on Communication / Telemetry Loss}
\label{sec:sw-comm-loss}

Loss of the operator control link triggers a controlled deceleration rather than an abrupt halt, avoiding instability (e.g. tip-over) at speed.

\subsubsection{Collision-Avoidance / Overcurrent Stop Conditions}
\label{sec:sw-overcurrent}

Each wheel driver auto-deactivates above 5\,\si{\ampere}, protecting against stalls, obstructions, or terrain collisions.

An impact-detection mechanism based on current-spike monitoring (main/arm sensors) combined with IMU data is under evaluation, since current alone spikes during normal high-load events (rocks, slopes, aggressive manoeuvres) as well as impacts. \textit{Status: under consideration, not yet implemented.}

\subsubsection{Reliability Argument}
\label{sec:sw-reliability}

Reliability comes from layered, partially-independent mechanisms: the ESP-based CAN watchdog operates independently of the main computer, so a software crash still results in a safe stop; graceful software responses (lock, rampdown, watchdog takeover) handle non-critical faults without invoking the hardware E-Stop; and if any software mechanism fails to trigger, the hardware E-Stop (Sec.~\ref{subsec:emergency_stop}) remains as an independent fallback.
\todo[inline]{Add quantitative evidence if fault-injection tests were run, e.g. killing the main computer process and confirming watchdog engagement within the expected timeout.}