% =============================================================================
% tables/lessons_learnt.tex  -  Master Lessons Learnt table
% Teams: PM / Status: placeholder rows (curated in Phase 4)
%
% OWNERSHIP: this table is edited directly by its curator - the selected
% lessons are inserted all at once, replacing the placeholder rows below.
% Teams send candidates to the curator instead of editing this file. Row
% shape (6 cells):
%   ID & Title & Root cause & Description & Recommendation & Impact \\
% ID scheme: LL-<TEAM>-NN (e.g. LL-SUS-01) to keep provenance visible.
%
% The rows below are placeholders sized to reserve ~1 page in the landscape
% appendix - not real lessons. Replace them wholesale once curated.
% =============================================================================

\begingroup\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{longtable}{C{1.6cm} L{3.0cm} L{4.5cm} L{6.5cm} L{5.0cm} L{3.0cm}}
    \caption{Lessons Learnt}
    \label{tab:lessons_learnt} \\
    \toprule
    \textbf{ID} & \textbf{Title} & \textbf{Root Cause} & \textbf{Description}
        & \textbf{Recommendation} & \textbf{Impact} \\
    \midrule
    \endfirsthead
    \multicolumn{6}{c}{\small\itshape (continued from previous page)} \\
    \toprule
    \textbf{ID} & \textbf{Title} & \textbf{Root Cause} & \textbf{Description}
        & \textbf{Recommendation} & \textbf{Impact} \\
    \midrule
    \endhead
    \bottomrule
    \endlastfoot

    LL-TBD-01 & Placeholder title & Placeholder root cause. & Placeholder description of the lesson learnt. & Placeholder recommendation for future seasons. & Placeholder impact assessment. \\
    LL-TBD-02 & Placeholder title & Placeholder root cause. & Placeholder description of the lesson learnt. & Placeholder recommendation for future seasons. & Placeholder impact assessment. \\
    LL-TBD-03 & Placeholder title & Placeholder root cause. & Placeholder description of the lesson learnt. & Placeholder recommendation for future seasons. & Placeholder impact assessment. \\
    LL-TBD-04 & Placeholder title & Placeholder root cause. & Placeholder description of the lesson learnt. & Placeholder recommendation for future seasons. & Placeholder impact assessment. \\
    LL-TBD-05 & Placeholder title & Placeholder root cause. & Placeholder description of the lesson learnt. & Placeholder recommendation for future seasons. & Placeholder impact assessment. \\
    LL-TBD-06 & Placeholder title & Placeholder root cause. & Placeholder description of the lesson learnt. & Placeholder recommendation for future seasons. & Placeholder impact assessment. \\
    LL-TBD-07 & Placeholder title & Placeholder root cause. & Placeholder description of the lesson learnt. & Placeholder recommendation for future seasons. & Placeholder impact assessment. \\
    LL-TBD-08 & Placeholder title & Placeholder root cause. & Placeholder description of the lesson learnt. & Placeholder recommendation for future seasons. & Placeholder impact assessment. \\

\end{longtable}
\endgroup
