% =============================================================================
% tables/rio_table.tex  -  RIO register (risks + opportunities + issues)
%
% Rendered as a landscape appendix page (sections/appendix_rio.tex), which
% widens \textwidth/\linewidth locally before \input-ing this file - the
% pdflscape `landscape` environment only rotates the page, it does not
% widen \linewidth on its own, and longtable's own \LTleft/\LTright margin
% trick does not compose reliably with pdflscape (produces bogus overfull
% warnings) - do not reintroduce it here. Single table per the official
% Final Report template. 8 pt font is allowed in RIO tables only (hence
% \footnotesize under the 10 pt document font).
% Owned centrally (PM) - IDs MUST match the Preliminary Report:
%   R-01..R-10, O-01, I-01..I-03. Highlight and justify removals/additions.
%
% Phase 2 (rio/port-preliminary): rows below are carried over verbatim from
% the Preliminary Report's risk register (Table 21) and opportunities/
% issues registers (Tables 22-23), reshaped into this table's single-table
% column set. Two things still need PM review before this counts as the
% "second iteration" the rubric asks for:
%   1. The "Impact type" column did not exist in the Preliminary (which
%      only had a free-text Impact description). Values below are inferred
%      from that description against the template's allowed list (Time,
%      Cost, Scope, Quality, Resources, Economic, Managerial, Technical,
%      Generic) - NOT team-assessed. Verify each one.
%   2. L/S/RI for O-01 and I-01..I-03 are marked "?": the Preliminary
%      never assessed likelihood/severity for opportunities or issues, only
%      for risks. This is exactly the gap the jury flagged ("Issues and
%      Opportunities should have their likelihood and severity tracked as
%      well") - assign real L/S values before freeze, don't leave as "?".
%   3. Risk descriptions/mitigations are otherwise unchanged from the
%      Preliminary. The jury also flagged several as too generic
%      (e.g. R-01: "determine which system you're considering as
%      critical"). A low score follows if the majority of risks are
%      unchanged between iterations - this table is a starting point for
%      the second-iteration pass, not the finished assessment.
%
% Update (2026-07-21): second-iteration pass addressing point 3 above.
%   - R-01, R-02, R-03 rewritten with concrete, subsystem-specific
%     descriptions/mitigations (was generic boilerplate flagged by jury).
%   - R-06 downgraded 9->3 (L 3->1): cross-subsystem integration verified
%     end-to-end; residual risk kept open only for future hardware swaps.
%   - R-11..R-16 added (new risks identified since Preliminary): R-11
%     setup/teardown schedule overrun, R-12 config drift practice->finals,
%     R-13 fragmented subsystem observability, R-14 wheel bracket fracture
%     risk, R-15 end-effector camera blind spots, R-16 stereo VIO drift
%     under chassis vibration. None supersede/replace an existing ID.
%   - R-15's mitigation is still a placeholder pending input from the
%     manipulation lead (Marta) - resolve before freezing this table.
%
% Row shape (11 cells):
%   ID & Name & Description & Category & Impact type & Owner
%      & L & S & RI & Response & Actions \\
% RI cell colour: \riskhigh-equivalent \cellcolor{red!40} >=15,
%   \cellcolor{orange!40} 6-14, \cellcolor{green!30} <=5.
% =============================================================================

\begingroup\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{longtable}{C{1.0cm} L{2.3cm} L{5.05cm} L{1.7cm} C{1.6cm} L{1.9cm} C{0.6cm} C{0.6cm} C{0.8cm} L{2.0cm} L{4.1cm}}
    \caption{Qualitative risks, opportunities, and issues assessment (second iteration)}
    \label{tab:rio} \\
    \toprule
    \textbf{ID} & \textbf{Name} & \textbf{Description} & \textbf{Cat.}
        & \textbf{Impact} & \textbf{Owner} & \textbf{L} & \textbf{S}
        & \textbf{RI} & \textbf{Response} & \textbf{Actions} \\
    \midrule
    \endfirsthead
    \multicolumn{11}{c}{\small\itshape (continued from previous page)} \\
    \toprule
    \textbf{ID} & \textbf{Name} & \textbf{Description} & \textbf{Cat.}
        & \textbf{Impact} & \textbf{Owner} & \textbf{L} & \textbf{S}
        & \textbf{RI} & \textbf{Response} & \textbf{Actions} \\
    \midrule
    \endhead
    \bottomrule
    \endlastfoot

    R-14 & Wheel bracket unreliability & Original plastic wheel mounts can fracture from even a small collision, risking loss of mobility mid-run. & Risk & Technical & Chassis Lead & 4 & 4 & \cellcolor{red!40}16 & Mitigate & Replaced plastic mounts with machined metal wheel brackets; validate under drop/impact testing before competition. \\
    R-15 & End-effector camera blind spots & Shadows or low-light conditions can degrade the end-effector camera's usefulness during fine manipulation tasks. & Risk & Technical & Manipulation Lead & 4 & 4 & \cellcolor{red!40}16 & Mitigate & \textit{TODO (Marta): define concrete mitigation.} \\
    R-01 & Critical subsystem failure (mobility drivetrain / power distribution / manipulator actuation) & Mechanical or electrical failure of a mission-critical node during competition operation, resulting in loss of functional capability and potential task interruption. & Risk & Technical & Lead Engineer & 3 & 4 & \cellcolor{orange!40}12 & Mitigate & Maintain a spare-parts stock (drive motors, actuators, connectors) matched to the named critical subsystem(s), keep documented swap procedures with target repair times, and validate them via a fault-injection drill before competition. \\
    R-02 & Transport defects & Shock and handling loads during transit to the competition site risk physical damage to rover assemblies before operations. & Risk & Technical & Logistics Mgr. & 3 & 4 & \cellcolor{orange!40}12 & Mitigate & Palletized transport with modular, disassemblable packaging; foam-cut transit case; strain-relief/locking connectors; functional pre-run checklist executed on arrival before first power-on. \\
    R-03 & Overheating & Electronics/motors under high thermal load (ambient above \qty{30}{\celsius}) risk performance degradation and reduced reliability. Direct sun, high ambient temperatures, dust-clogged vents, or a fan failure could push bay temperature past safe limits for the mini-PC, monitors, or microcontroller mid-mission. & Risk & Technical & Hardware Eng. & 3 & 4 & \cellcolor{orange!40}12 & Mitigate & Sensor monitoring, power-saving mode, and active cooling designed for \qtyrange{40}{50}{\celsius}. Add thermostatic NTC-driven PWM fan control plus the existing bay-temperature ROS~2 topic for early detection, with a hard shutdown/alert threshold; run a pre-competition dust/heat soak test. \\
    R-11 & Setup/teardown schedule overrun & Mast assembly, antenna alignment, and the full boot/discovery sequence taking longer than budgeted can cost mission time or points independent of any technical fault. & Risk & Time & Ground Control Team & 3 & 4 & \cellcolor{orange!40}12 & Mitigate & Time the full setup sequence in rehearsal, set a hard target duration, and pre-stage/label cabling to remove decision time during actual setup. \\
    R-12 & Configuration drift between practice and finals & An untracked overnight change (e.g.\ ROS\_DOMAIN\_ID, a QoS profile, the Discovery Server address) can break something that worked in practice runs, with no audit trail to quickly identify what changed. & Risk & Technical & Software Lead & 3 & 4 & \cellcolor{orange!40}12 & Mitigate & Version-controlled, checksummed configuration files (env files, docker-compose) with an automated diff check integrated into the pre-run checklist, replacing informal reliance on prior working states. \\
    R-13 & Fragmented subsystem health/observability & Individual subsystems (link, thermal, time sync, discovery) each log independently, with nothing correlating them live. Small degradations --- creeping packet loss, Jetson thermal throttle, discovery-server queue backlog --- can stack invisibly until they surface together as a hard-to-diagnose failure under time pressure. & Risk & Technical & Software Lead & 3 & 4 & \cellcolor{orange!40}12 & Mitigate & Build a single ground-station dashboard panel aggregating link RSSI/loss, bay temperature, clock offset, and node liveliness in one glance; treat this as closing a process gap, not a component gap. \\
    R-04 & Limited prior competition experience & First ERC participation and incomplete familiarity with rule nuances risk lower execution efficiency and increased procedural errors. & Risk & Generic & Team Lead & 5 & 2 & \cellcolor{orange!40}10 & Accept & Regular consultations with domain specialists and mentors. \\
    R-05 & Control-logic robustness issues & Singularities and hardcoded logic paths in autonomy/control software risk operational instability and reduced task reliability. & Risk & Technical & Developer & 3 & 3 & \cellcolor{orange!40}9 & Mitigate & Refactor control logic to remove hardcoded paths and implement failsafe/fallback algorithms; add unit and singularity-boundary tests. \\
    O-01 & New-team perspective & As a new team, we can approach design choices without legacy constraints and propose unconventional yet effective solutions. & Opportunity & Generic & Team Lead & ? & ? & ? & Enhance & Prioritise fast concept validation; keep an innovation track in design reviews. \\
    I-01 & Time shortage & Limited available time across parallel development streams can delay verification and integration. & Issue & Time & Project Mgr. & ? & ? & ? & Mitigate & Reprioritise backlog weekly and protect integration/test windows. \\
    I-02 & Motor delivery delay & Delayed motor shipment prevents suspension assembly start and shifts downstream integration milestones. & Issue & Time & Suspension Lead & ? & ? & ? & Mitigate & Re-sequence tasks, track suppliers daily, prepare alternate sourcing. \\
    I-03 & Burned camera module & Failed camera hardware blocks early development and validation of vision algorithms. & Issue & Technical & Perception Lead & ? & ? & ? & Mitigate & Replace module, add electrical protection checks, continue with recorded datasets in parallel. \\

\end{longtable}
\endgroup
